Artificial ecosystem selection to deduce the mapping between microbial community structure and ecosystem function

### 2020-10-23 Manuscript/manuscript.Rmd
update presentation
update manuscript text

To test whether there was a significant change in CH~4~ oxidation rate (k) as a response to selection, we tested the deviation between the positive and neutral selection lines over multiple passages. We calculated deviation as the difference in the mean oxidation rate between the positive and neutral treatment within each passage. The standard errors of the deviations were calculated as the square root of the sum of the squared errors of the positive and neutral lines. We then fit an ordinary least squares regression model taking into account the standard errors of the deviations. The model was fit using the `rma` function from the `metafor` package in `r` (Viechtbauer 2010).

@@

To test the heritability of CH~4~ oxidation rate as an ecosystem property, we calculated narrow-sense heritability ($h^2$) as the regression of offspring on mid-parent (Goodnight 2000, Falconer 1997). The mid-parent was the mean for all three selected jars and the offspring was the mean for all jars produced by those parents.

@@

@@

ggsave('new_herit_fig.pdf', width = 5, height = 3)

>>>>

To test whether there was a significant change in CH~4~ oxidation rate (k) as a
response to selection, we tested the deviation between the positive and neutral
selection lines over multiple passages. We calculated deviation as the
difference in the mean oxidation rate between the positive and neutral
treatment within each passage. The standard errors of the difference were
calculated as the square root of the sum of the squared errors of the positive
and neutral lines. We then fit an ordinary least squares regression model
taking into account the standard errors of the deviations. The model was fit
using the `rma` function from the `metafor` package in `r` (Viechtbauer 2010).

@@

To estimate the proportion of variance in ecosystem function due to additive
genetic variance of the microbial communtiy, we applied the Breeder's equation
to the results of our selection experiment. the heritability of
CH~4~ oxidation rate as an ecosystem property, we calculated narrow-sense
heritability ($h^2$) as the regression of offspring on mid-parent (Goodnight
2000, Falconer 1997). The mid-parent was the mean for all three selected jars
and the offspring was the mean for all jars produced by those parents.

@@

Possible tests:

- Random forest or gradient boosting to predict Positive vs. Neutral.

@@
